Comparison of Catalogs

### 2024-07-31 compare/compare.qmd
Minor fixes

1.  $R^2$: Measures the proportion of variance explained by the linear model.
2.  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.[^1]
3.  Pearson Correlation $\rho$: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1. [^2]

[^1]: Fitting can be done using the uncertainties as weights. To get the standard weighting of 1/unc\^2, assuming Gaussian errors, the weights to pass to the fitting are 1/unc.

@@

Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers with $sigma > 3$

@@

<!-- -->

-   Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.

@@

```{python}
dt["log_a26"] = np.log10(dt["a26_1"].data)
dt["log_a26"].unit = u.arcmin
dt["log_R1"] = np.log10(dt["R1"].data)
dt["log_R1"].unit = u.arcmin
dt["log_R1"].info
```

@@

```{python}
temp.describe()
```

@@

temp = dt[["diff_K_mag"]].to_pandas()
c = temp["diff_K_mag"]
up_clip = c.mean() + 3*c.std()
low_clip = c.mean() - 3*c.std()
temp["Percentage Change, after 3 sigma clip [%]"] = temp["diff_K_mag"].clip(low_clip, up_clip)
temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
temp.describe()
```

@@

## Absorpsion

@@

## Internal

```{python}
plt.scatter(dt["AB_int"],dt["AI"],)
plt.xlabel(f"LCV, AB_int [{dt['AB_int'].unit}]")
plt.ylabel(f"HECATE, AI [{dt['AI'].unit}]")
plt.yscale("log")
plt.show()
```

```{python}
sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
```
:::

@@

```{python}
# Create a pair grid 
sns.pairplot(sfr_data, corner=True)
plt.show()
```

@@

```{python}
temp.rename(columns={"diff_M":"Percantage Change [%]"}, inplace = True)
```
```{python}
temp.describe()
```
## Heatmap

>>>>

1.  $R^2$: Measures the proportion of variance explained by the linear model.
2.  Slope of the Fitted Line: Should be close to 1 for a 1-1 correlation.[^1]

[^1]: Some data seem to have a very good linear correlation but they have many outliers. This is why we will clip the outliers with $\sigma > 3$

3.  Pearson Correlation $\rho$: Measures the strength and direction of the linear relationship between two variables, ranging from -1 to 1. [^2]

@@

@@

-   Kernel Density Estimate (KDE) plot: The KDE plot visually represents the distribution of data, providing insights into its shape, central tendency, and spread.

5.  Percentage change: We can calculate the percentage change of the data for each galaxy and then we can see if the data are similar, based on minimum, the maximum and the mean value of the difference.

@@

```{python}
dt["log_a26"] = np.log10(dt["a26_1"].data)
dt["log_a26"].unit = u.arcmin
dt["log_R1"] = np.log10(dt["R1"].data)
dt["log_R1"].unit = u.arcmin
```

@@

```{python}
temp.describe(percentiles=[])
```

@@

temp = dt[["diff_K_mag"]].to_pandas()
c = temp["diff_K_mag"]
up_clip = c.mean() + 3*c.std()
low_clip = c.mean() - 3*c.std()
temp["Percentage Change, after 3 sigma clip [%]"] = temp["diff_K_mag"].clip(low_clip, up_clip)
temp.rename(columns={"diff_K_mag":"Percentage Change [%]"}, inplace=True)
temp.describe(percentiles=[])
```

@@

## Absorption

@@

## Internal
```{python}
sns.jointplot(x=dt["AB_int"], y=dt["AI"], kind="reg",)
plt.xlabel(f"LCV, AB_int [{dt['AB_int'].unit}]")
plt.ylabel(f"HECATE, AI [{dt['AI'].unit}]")
plt.show()
```
Here we can see an attempt to correlate the internal absorption of the two catalogs, however as it is very clear, there is no correlation, since even their distributions are not similar.
:::

@@

```{python}
# Create a pair grid 
plt.figure(figsize=(10, 8))
sns.pairplot(sfr_data, corner=True)
plt.show()
```

@@

```{python}
temp.rename(columns={"diff_M":"Percantage Change [%]"}, inplace = True)
```
```{python}
temp.describe(percentiles=[])
```
## Heatmap
